\bf A Concise Survey on Statistical Analysis in Bike Lane Research

### 2023-12-15 Manuscript/Manuscript.tex
made last edits for final draft

{\title{\bf A Concise Survey on Statistical Analysis in Bike Lane Research}
  \author{Zoe Macris\\
  University of Connecticut}
\date{December 2023}
  \maketitle}

@@

\keywords{Bike Lanes, Regression Analysis, Binary Regression Models, Multiple Level Regression Analysis, Zero-Inflated Poisson, Generalized Linear Model}

>>>>

{\title{\bf A Concise Survey on Statistical Analysis Methods in Bike Lane Research}
  \author{Zoe Macris\\
  University of Connecticut}
\date{December 2023}
  \maketitle}

@@

\keywords{Cycling Infrastructure, Regression Analysis, Binary Regression Models, Multiple Level Regression Analysis, Zero-Inflated Poisson, Generalized Linear Model}
